---
title: "HW1-BS"
author: "Brooke Sasia"
format: html
editor: visual
---

# Homework 1: R Refresher

```{r, message = FALSE}
library(dplyr)
library(ggplot2)
library(psych)
```

I'm a third year grad student in the Clinical Psychology PhD program advised by Dr. James Li! My research interests include genetic and environmental factors underlying externalizing behaviors across development.

### Mean miles per gallon
```{r}
mean_mpg <- mean(mtcars$mpg)
```

The mean miles per gallon for cars in the mtcars dataset is: `r mean_mpg`.

### Number of cars with mpg >30
```{r}
filter(mtcars, mpg > 30) %>% 
  count()

describe(mtcars$mpg)
```

Of the 32 cars in the mtcars dataset, only 4 cars get gas mileage greater than 30 miles per hour.

### Correlation between miles per gallon and number of cylinders
```{r}
mtcars %>% 
  select(mpg, cyl) %>% 
  corr.test()
```

### Graph of association between mpg and cylinders in mtcars
```{r, message = F}
ggplot(mtcars, aes(x = mpg, y = cyl))+
      geom_point() + 
      geom_smooth(method = "lm", se = FALSE) + 
  xlab("Miles per gallon") + 
  ylab("Number of cylinders") + 
  ggtitle("Association between miles per gallon \n and cylinders in mtcars") + 
  theme_bw(base_size = 20) + 
  theme(axis.text.x = element_text(size = 14, face = "bold"), 
        axis.text.y = element_text(size = 14, face = "bold"), 
        axis.title = element_text(size = 18, face = "bold"), 
        axis.line = element_line(color = "black"), 
        axis.ticks = element_line(color = "black"), 
        plot.title = element_text(hjust = 0.5, face = "bold"), 
        panel.border = element_blank(), 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(), 
        text = element_text(family = "Times New Roman")) + 
  scale_x_continuous(breaks = round(seq(min(10), max(35), by = 5))) + 
  scale_y_continuous(breaks = round(seq(min(2), max(10), by = 2)))
```

The above graph shows that there is a strong negative correlation between number of cylinders and miles per gallon (*r* = -0.85, *p* < .01) such that as the number of cylinders decreases, miles per gallon increases.

