---
title: "HW1-SS"
format: html
editor: visual
---

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
library(psych)
```

My name is Sarah Salas. I am from Texas and I have a 3-legged cat named Peach.

```{r}
mean_mpg <- mean(mtcars$mpg) # having the = instead of <- is fine here but might need the <- for it to be less ambiguous
```

The mean miles per gallon for cars in the mtcars dataset is: `r mean_mpg`

```{r, message=FALSE}
# write code that will count the number of cars in the dataset that get >30 miles per gallon and return that number below the chunk
mtcars <- mtcars
mpg_30 <- subset(mtcars, mpg > 30)
nrow(mpg_30)
```

The proportion of cars in the mtcars dataset that get \>30 mpg is: `r nrow(mpg_30)/nrow(mtcars)`

```{r}
correlation <- cor(mtcars$mpg, mtcars$cyl, method = 'pearson')
```

The pearson correlation between miles per gallon and number of cylinders of the cars in the database is: `r correlation`

```{r}
data(mtcars)
ggplot(mtcars, aes(x = cyl, y = mpg))+
      geom_point() + 
      geom_smooth(method = "lm", se = FALSE)
```

The graph shows that there is a negative relationship between cylinders and miles per gallon. The more cylinders the fewer miles per gallon we can expect.
